### 2016-10-05 Documents/bootcamp_practice_3.tex
updated HW 3

\begin{parts}
\item Explain the \texttt{import} statement.
\item What type of object is {\tt data}?
\item Why does the last line have {\tt pd} prior to the {\tt DataFrame} function?
\item What type of object is {\tt weo}?
\item How many rows does it have?  Columns?
\item What {\tt dtypes} are the variables/columns?  What does this mean?
\item {\it Challenging.\/}
What are each of these expressions?  What type?
\begin{verbatim}
weo['Year']
weo[['Year']]
weo[[3]]
\end{verbatim}
\item {\it Challenging.\/}
Find and apply a method to convert {\tt weo['Year']} to type {\tt float}.
{\it Hint:\/} The method begins with the letter {\tt a}.
\item Describe the result of the statement \texttt{t = weo.tail(3)}.
What kind of object is \texttt{t}?  What does it look like?
\item How would you create a new dataframe that consists of the first 4 rows of \texttt{weo}?
\item What type of object is \texttt{weo['BRA']}?
\item Create a new variable equal to the ratio of Brazil's GDP per capita to Japan's.
\item {\it Challenging.\/}
Use the {\tt drop()} method to eliminate this (new) variable from the dataframe.
\item What are {\tt weo}'s row and column labels?
\item Set the index equal to the {\tt Year} variable.
\item Change the names of the other variables to Brazil, Japan, and United States.
\item Export the dataframe to an Excel spreadsheet.
\item What method would you use to compute the mean for each country?
What are the means?
\item {\it Challenging.\/}
How would you compute means across countries for each year?
\item Plot the data by applying a {\tt plot} method to {\tt weo}.
\item {\it Challenging.\/} Change the colors of the lines to green (Brazil), red (Japan),
and blue (US).
\item {\it Challenging.\/}
Do the same plot with a log scale.
{\it Hint:\/} Read the documentation for the plot method.
\item Plot Brazil on its own.
\end{parts}

@@

\vspace{0.1in}
\centerline{\url{http://pages.stern.nyu.edu/~dbackus/Data/Data-Bootcamp-entry-poll_s16.csv}}
\vspace{0.1in}

>>>>

\begin{parts}
\item Explain the \texttt{import} statement.
\item What type of object is {\tt data}?
\item Why does the last line have {\tt pd} prior to the {\tt DataFrame} function?
\item What type of object is {\tt weo}?
\item How many rows does it have?  Columns?
\item What {\tt dtypes} are the variables/columns?  What does this mean?
\item {\it Challenging.\/}
What are each of these expressions?  What type?
\begin{verbatim}
weo['Year']
weo[['Year']]
weo[[3]]
\end{verbatim}
\item {\it Challenging.\/}
Find and apply a method to convert {\tt weo['Year']} to type {\tt float}.
{\it Hint:\/} The method begins with the letter {\tt a}.
\item Describe the result of the statement \texttt{t = weo.tail(3)}.
What kind of object is \texttt{t}?  What does it look like?
\item How would you create a new dataframe that consists of the first 4 rows of \texttt{weo}?
\item What type of object is \texttt{weo['BRA']}?
\item Create a new variable equal to the ratio of Brazil's GDP per capita to Japan's and add it to the DataFrame.
\item {\it Challenging.\/}
Use the {\tt drop()} method to eliminate this (new) variable from the dataframe.
\item What are {\tt weo}'s row and column labels?
\item Set the index equal to the {\tt Year} variable.
\item Change the names of the other variables to Brazil, Japan, and United States.
\item Export the dataframe to an Excel spreadsheet.
\item What method would you use to compute the mean for each country?
What are the means?
\item {\it Challenging.\/}
How would you compute means across countries for each year?
\item Plot the data by applying a {\tt plot} method to {\tt weo}.
\item {\it Challenging.\/} Change the colors of the lines to green (Brazil), red (Japan),
and blue (US).
\item {\it Challenging.\/}
Do the same plot with a log scale.
{\it Hint:\/} Read the documentation for the plot method.
\item Plot Brazil on its own.
\end{parts}

@@

\vspace{0.1in}
\centerline{\url{https://raw.githubusercontent.com/NYUDataBootcamp/Materials/master/Data/entry_poll_fall16.csv}}
\vspace{0.1in}
